---
title: "p8105_hw1_hs3163"
author: "Hao Sun"
date: "9/14/2019"
output: gitl_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)

```

## Problem 1

Create a data frame comprised of:

1. a random sample of size 8 from a standard Normal distribution
2. a logical vector indicating whether elements of the sample are greater than 0
3. a character vector of length 8
4. a factor vector of length 8, with 3 different factor “levels”

```{r problem1}
#Set the seed for the random Norma distribution
set.seed(1)
problem1_df = tibble(
  #the first vector is a random sample of size 8 from a standard Normal distribution
  vec_random_sample = (x = rnorm(8) ),
  #the second vector is the a character vector of length 8 indexing the sample from normal distribution
  vec_char = c("first", "second", "third", "forth","fifth","sixth","seventh","eighth"),
  #the third vector is the logical vector that used to determined whether elements of the sample are greater than 0
  vec_logical = vec_random_sample > 0 ,
  #the forth vector is the factor that comprised of three levels.
  vec_factor = factor(c("low", "low", "low", "middle","middle","high","high","high"))
)
  
problem1_df
```
Try to take the mean of each variable in your dataframe. What works and what doesn’t?

In some cases, you can explicitly convert variables from one type to another. Write a code chunk that applies the as.numeric function to the logical, character, and factor variables (please show this chunk but not the output). What happens, and why? Does this help explain what happens when you try to take the mean?


```{r}

as.numeric(problem1_df$vec_char)
as.numeric(problem1_df$vec_logical)
as.numeric(problem1_df$vec_factor)


```





## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
