---
title: "p8105_hw1_hs3163"
author: "Hao Sun"
date: "9/14/2019"
output: gitl_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)

```

## Problem 1

Create a data frame comprised of:

1. a random sample of size 8 from a standard Normal distribution
2. a logical vector indicating whether elements of the sample are greater than 0
3. a character vector of length 8
4. a factor vector of length 8, with 3 different factor “levels”

```{r problem1}
problem1_df = tibble(
  vec_random_sample = ordered(x = rnorm(8) ),
  vec_char = c("first", "second", "third", "forth","fifth","sixth","seventh","eighth"),
  vec_logical = vec_random_sample > 0 ,
  vec_factor = factor(c("low", "low", "low", "median","median","high","high","high"))
)
  
problem1_df
vec_random_sample = ordered(x = rnorm(8) )
    vec_random_sample 

```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
